Bacon: A GPU Programming Language With Just in Time Specialization

### 2011-05-29 doc/Paper/Paper.tex
Paper abstract.

@@

This paper describes Bacon, a programming language that makes it
easier to write high performance kernels to run on for OpenCL
compatible general purpose GPUs. The design and implementation is
described, and benchmarks are given showing performance gains over
comparable programs written directly in OpenCL C.

>>>>

% Keywords:
%   data parallel, gpu, opencl, jit specialization

@@

This paper describes Bacon, a data-parallel programming system
targetting OpenCL-compatible graphics processors. This system is built
upon the existing OpenCL standard in order to make it easier for
programmers to write high performance kernels for GPU accelerated
applications. The OpenCL C syntax is extended into a new language,
Bacon C, intended to make development significantly more convienient
and enabling pre-optimizations based on just-in-time specialization as
this code is compiled via OpenCL at runtime.

Benchmarks are provided for matrix multiplication comparing a Bacon
implementation to versions using OpenCL directly. Speedups are
demonstrated both for naive implementations and when comparing a naive
Bacon implementation to a hand-vectorized OpenCL kernel. This latter
result demonstrates the benefit of the total loop unrolling enabled by
just-in-time specialization. Additionally, a Bacon implementation of a
more complex computation, stereo disparity, is considered.
